Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-08-02 manuscript/appendix.Rmd
updated table S1
fixed captions and column headings in SI tables

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/climate_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE, caption = "Table S1. Climate variable definitions, sources, and abbreviations", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1, width = "2.5cm") %>%
  column_spec(2, width = "5cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "7cm") %>%
  column_spec(5, width = "2cm") %>%
  column_spec(6, width = "5cm") %>%
  kableExtra::footnote(number = c("Hijmans et al. (2005)", "Fick et al. (2017)", "Harris et al. (2017)", "Abatzoglou et al. (2018)"), footnote_as_chunk = TRUE)

@@

\blandscape
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S3 <- read.csv("tables_figures/r2_table1.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S3, format = "latex", booktabs = TRUE, caption = "Table S2. Model form, delta AIC, and R2 for each climate variables as a single fixed effect in models for each C flux. Model forms include first-order linear (Lin), second-order polynomial (Poly), and logarithmic (Log).", caption.short = "Table S2. Model form, delta AIC and R2 for each climate variables as a single fixed effect in models for each C flux") %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  add_header_above(c(" ", "Latitude"=3, "MAT"=3, "MAP"=3, "T Seas"=3, "P Seas"=3, "ATR"=3, "Solar R"=3, "AI"=3))
```

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S4 <- read.csv("tables_figures/r2_table2.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S4, format = "latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  add_header_above(c(" ", "Cloud"=3, "AFD"=3, "AWD"=3, "PET"=3, "VPD"=3, "Max VPD"=3, "WSM"=3, "LGS"=3))
```
\elandscape

@@

\newpage
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S3 <- read.csv("tables_figures/best_models_each_flux.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S3, format = "latex", booktabs = TRUE, caption = "Table S5. Best models by carbon flux. Models where delta AIC </= 2 are presented", caption.short = "Table S5. Best models by carbon flux", escape = F) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  collapse_rows(columns = 1, latex_hline = "major")
```

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/climate_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE, caption = "Table S1. Climate variable definitions, sources, and abbreviations", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1, width = "2.5cm") %>%
  column_spec(2, width = "5cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "7cm") %>%
  column_spec(5, width = "2cm") %>%
  column_spec(6, width = "5cm") %>%
  kableExtra::footnote(number = c("Hijmans et al. (2005)", "Fick et al. (2017)", "Harris et al. (2017)", "Abatzoglou et al. (2018)"), footnote_as_chunk = TRUE) %>%
  kableExtra::footnote(symbol = "The WorldClim version used was up-to-date at the time of analysis", footnote_as_chunk = TRUE)

@@

\blandscape
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S3 <- read.csv("tables_figures/r2_table1.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S3, format = "latex", booktabs = TRUE, caption = "Table S2. Model form, $\\Delta$AIC, and R$^{2}$ for each climate variables as a single fixed effect in models for each C flux. Model forms include first-order linear (Lin), second-order polynomial (Poly), and logarithmic (Log).", caption.short = "Table S2. Model form, $\\Delta$AIC and R$^{2}$ for each climate variables as a single fixed effect in models for each C flux", escape = F) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  add_header_above(c(" ", "Latitude"=3, "MAT"=3, "MAP"=3, "T Seas"=3, "P Seas"=3, "ATR"=3, "Solar R"=3, "AI"=3))
```

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S4 <- read.csv("tables_figures/r2_table2.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S4, format = "latex", booktabs = TRUE, escape = F) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  add_header_above(c(" ", "Cloud"=3, "AFD"=3, "AWD"=3, "PET"=3, "VPD"=3, "Max VPD"=3, "WSM"=3, "LGS"=3))
```
\elandscape

@@

\newpage
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S3 <- read.csv("tables_figures/best_models_each_flux.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S3, format = "latex", booktabs = TRUE, caption = "Table S5. Best models by carbon flux. Models where $\\Delta$AIC </= 2 are presented", caption.short = "Table S5. Best models by carbon flux", escape = F) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  collapse_rows(columns = 1, latex_hline = "major")
```
